Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
Added references

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890 observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess, we will infer $\nu_\mathrm{max}$ and $\Delta\nu$
using only one month of \kepler\ data and compare our results to the results
inferred from the full 4 year baseline of the mission.
For KIC~11615890, the published asteroseismic parameters based on the full
dataset are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celerite\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.
\dfmtodo{Add some more discussion here.}

@@

Our background is in studying transiting exoplanets, a field which has only recently begun
to adopt full covariance matrices in analyzing the noise in transiting planet lightcurves.
One promising early attempt at accounting for correlated noise was the wavelet approach
of Carter \& Winn (2010).  Their technique allowed for a power-law spectrum for the
noise scaling as $\omega^{-\alpha}$, which unfortunately is not a normalizable, nor
physically-accurate, description of stellar variability.  Their approach runs in
${\cal O}(N)$ time for $\alpha=1$, which is `flicker' or pink noise;  however, this
particular type of noise overpredicts the power spectrum at low frequency compared
to the granulation power spectrum.  It also cannot describe quasi-periodic noise.

>>>>

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890 observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess \citep{Campante2016}, we will infer $\nu_\mathrm{max}$ and $\Delta\nu$
using only one month of \kepler\ data and compare our results to the results
inferred from the full 4 year baseline of the mission.
For KIC~11615890, the published asteroseismic parameters based on the full
dataset are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celerite\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.
\dfmtodo{Add some more discussion here.}

@@

Our background is in studying transiting exoplanets, a field which has only recently begun
to adopt full covariance matrices in analyzing the noise in transiting planet lightcurves.
One promising early attempt at accounting for correlated noise was the wavelet approach
of \citet{Carter2009}.  Their technique allowed for a power-law spectrum for the
noise scaling as $\omega^{-\alpha}$, which unfortunately is not a normalizable, nor
physically-accurate, description of stellar variability.  Their approach runs in
${\cal O}(N)$ time for $\alpha=1$, which is referred to as `flicker', $1/r$, or pink 
noise;  however, this particular type of noise overpredicts the power spectrum at low 
frequency compared to the Solar granulation power spectrum.  It also cannot describe 
quasi-periodic noise.
